{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-19 thesis/quicksand.tex
quicksand expt setup, test suite

In related work,
Portend \cite{portend} has already suggested combining data race analysis with preemption-driven artificial scheduling,
although it obtains its data-race candidates from a stand-alone, single-pass analysis.
In order to make sure we identify every one of a program's data races that could possibly arise under the given test case,
we must check many different interleavings to begin with,
perform the Portend approach for every data race we find,
which may in turn uncover more data races
(hidden in flow control paths reachable only through interleavings of the first race, perhaps),
and then continue model checking the multiple data races together
in a sort of bidirectional feedback loop between the two algorithms.
I will refer to data races that require model checking to expose to begin with as
{\em nondeterministic data races}. % TODO: rename, this name is awful
In the next section,
\cref{sec:quicksand-id} will show how I achieve this in Quicksand, and
\cref{sec:quicksand-soundness} will justify the technique's formal verification power.
In the evaluation (\cref{sec:quicksand-eval}),
\cref{sec:quicksand-eval-nondets} in particular will justify the need
for this feedback loop between model checking and data race analysis
by showing that many bugs require nondeterministic data races to expose.

@@

To address the problem of choosing meaningful preemption points,
I have developed an algorithm called {\em Iterative Deepening},
implemented in a wrapper program specific to Landslide called {\em Quicksand}.
Named after the analogous technique in chess artificial intelligence \cite{iterative-deepening-chess-ai},
Iterative Deepening
is a search strategy,
for exponentially-sized state spaces in general,
which
makes progressively deeper searches of the state space until the CPU budget is exhausted.
In this context, the depth roughly corresponds to the subset of preemption points used.
Hence, Quicksand
schedules multiple Landslide instances in parallel to
test many different subsets of the available preemption points,

@@

Note that Iterative Deepening is a {\em wrapper} algorithm around stateless MC.
A model checker is still used to test each state space, and other reduction techniques such as DPOR
are still applicable in each.
Moreover, because Iterative Deepening treats the set of preemption points as mutable,
it can add new preemption points reactively based on any runtime analysis.
Here
will focus on run-time data race analysis~\cite{tsan,fasttrack} as the mechanism for finding new preemption candidates.
The next section (\cref{sec:quicksand-soundness})
will prove that in fact,
in addition to statically-known synchronization preemption points,
this suffices to provide at least as strong verification guarantees as any other possible preemption point set.

@@

Given unlimited CPU time for testing,
one would always want to switch to the new maximal state space whenever adding a new preemption point.
The maximal state space is guaranteed to subsume all execution sequences reachable in any subset state space,
so considering any incomplete subset of the known preemption points would be duplicate work.
\Cref{alg:algorithm0} demonstrates this na\"ive approach.
It is seeded with the set of all statically-known synchronization API preemption points,
and invoked whenever a new data-race candidate is found.
%
The upcoming proofs in \cref{sec:quicksand-soundness},
being concerned with the verification guarantee provided when the search may complete within the CPU budget,
are based on this simple version of Iterative Deepening.
The user may also wish to configure her testing tool to prefer this approach, at her discretion,
such as when she believes all bugs have been fixed and wants a verification as fast as possible;
% TODO: clarify sec reference to -M flag
\cref{sec:quicksand-implementation} discusses this execution mode further.

@@

\begin{figure}[t]
        %\includegraphics[width=0.48\textwidth]{dr-jobs-v2.pdf}
        asdfsaf
        % TODO: put the figure form yr snake fight
	\caption[Quicksand incorporates data race reports as new preemption points at run-time.]
		{Quicksand incorporates data race reports as new preemption points at run-time,
		by managing the exploration of multiple state spaces,
		communicating with each MC instance to receive ETAs, data race candidates, and bug reports.
                %When an access pair is reported as a data race candidate,
                When a data race is reported,
                a new preemption point is added for each involved access,
                and new jobs are added for later testing,
                corresponding to different combinations of those with the existing preemption points.}
        \label{fig:new-dr-jobs}
\end{figure}

@@

% TODO: fix syntax hilight
% TODO check figure placement
% TODO check figure camption
\begin{figure}[t]
	\begin{center}
	\begin{tabular}{rll}
		& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
		& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
		\\
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		2 & \texttt{\hilight{olivegreen}{free}(x);} \\
		3 & & \texttt{\hilight{commentblue}{// x's memory reallocated}} \\
		4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
		6 & & \texttt{publish(y);} \\
		7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
	\end{tabular}
	\end{center}
	\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
	\label{fig:recycle}
\end{figure}

@@

% TODO smae as above
\begin{figure}[t]
	\begin{tabular}{rll}
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{publish(x);} & \\
		2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		3 & \texttt{\hilight{olivegreen}{free}(x);} \\
		4 & & \texttt{x2 = get\_published\_x();} \\
		5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
		6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
	\end{tabular}
	\caption{If a single-pass Limited HB analysis discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
	\label{fig:recycle-bug}
\end{figure}

@@

\begin{definition}[Reachability]
	A data race candidate, and its associated preemption point(s),
	are reachable if it will be identified by a model checker
	configured to preempt only on already-reachable preemption points.
\end{definition}

@@

\begin{itemize}
	\item {\bf Single state space, basic DPOR} ({\tt -C}):
		Runs a single instance of Landslide configured to preempt on all statically-known synchronization PPs.
		Corresponds to dBug's approach \cite{dbug-ssv}.
		Never adds any new preemption points based on data race reports.
	\item {\bf Single state space, ICB} ({\tt -I}):
		Runs a single instance of Landslide with preemption points as above,
		but running Iterative Context Bounding with BPOR (\cref{sec:landslide-icb})
		instead of plain DPOR.
		Corresponds to Chess's approach \cite{chess}.
		Requires either {\tt -C} or {\tt -M} (see below).
	\item {\bf Single state space, preempt-everywhere} ({\tt -0}, i.e., numeral zero):
		Runs a single instance of Landslide as above,
		but preempting on every shared memory access, not just synchronization.
		Corresponds to the approach of SPIN \cite{spin} and Inspect \cite{inspect}.
		May optionally be combined with {\tt -I}.
	\item {\bf Maximal state space mode} ({\tt -M})
		Runs the na\"{i}ve version of Iterative Deepening shown in \Cref{alg:algorithm0},
		i.e.,
		immediately abandons any state space whenever a superset of it exists.
		This results in always testing the maximal state space only, with no inherent parallelism,
		and optimizes for the fastest verification when the user has reason to believe no bugs will exist.
		No prior work implements this approach.
		Note that this mode was implemented after \cite{quicksand}'s publication,
		and I will feature it in the evaluation of transactional memory
		(\cref{sec:tm-eval}) rather than in this chapter.
\end{itemize}

@@

Preempt-everywhere mode (\cref{sec:quicksand-impl-modes})
imposes a heavy burden on Landslide on account of the sheer number of preemption points involved.
First of all, because there are separate tracing entrypoints for memory accesses and instructions ({\tt instrument.c}),
it cannot simply invoke the checkpointing routine (\cref{sec:landslide-timetravel}) immediately.
Also, we must still exclude thread-local and kernel (if testing userspace) or user (if testing kernelspace) accesses.
Rather,
the memory analysis (\cref{sec:landslide-memory}) invokes
{\tt maybe\_preempt\_here()} in {\tt pp.c}
for every access it would ordinary record for DPOR.
If the access is outside of the current stack frame,
and not part of the mutexes (unless {\tt TESTING\_MUTEXES}),
this sets a scheduler action flag {\tt preempt\_for\_shm\_here}
which makes preemption point identification treat it the same as a data race (\cref{sec:landslide-pps}).
{\tt check\_withins()} is also modified to never switch to allowlist mode.
Finally,
Landslide increases its heuristic constant for infinite loop detection (\cref{sec:landslide-infloop})
on the first interleaving from 4000 to $2^{20}$,
to account for the increased orders of magnitude in state space size.

@@

>>>>

In related work,
Portend \cite{portend} has already suggested combining data race analysis with preemption-driven artificial scheduling,
although it obtains its data-race candidates from a stand-alone, single-pass analysis.
In order to make sure we identify every one of a program's data races that could possibly arise under the given test case,
we must check many different interleavings to begin with,
perform the Portend approach for every data race we find,
which may in turn uncover more data races
(hidden in flow control paths reachable only through interleavings of the first race, perhaps),
and then continue model checking the multiple data races together
in a sort of bidirectional feedback loop between the two algorithms.
I will refer to data races that require model checking to expose to begin with as
{\em nondeterministic data races}. % TODO: rename, this name is awful
In the next section,
\cref{sec:quicksand-id} will show how I achieve this in Quicksand, and
\cref{sec:quicksand-soundness} will justify the technique's formal verification power.
In the evaluation, %(\cref{sec:quicksand-eval}),
\cref{sec:quicksand-eval-nondets} in particular will justify the need
for this feedback loop between model checking and data race analysis
by showing that many bugs require nondeterministic data races to expose.

@@

To address the problem of choosing meaningful preemption points,
I have developed an algorithm called {\em Iterative Deepening},
implemented in a wrapper program specific to Landslide called {\em Quicksand}.
Named after the analogous technique in chess artificial intelligence \cite{iterative-deepening-chess-ai},
Iterative Deepening
is a search strategy
for exponentially-sized state spaces, in general,
which
makes progressively deeper searches of the state space until the CPU budget is exhausted.
In this context, the depth roughly corresponds to the subset of preemption points used.
Hence, Quicksand
schedules multiple Landslide instances in parallel to
test many different subsets of the available preemption points,

@@

Note that Iterative Deepening is a wrapper algorithm around stateless MC.
A model checker is still used to test each state space, and other reduction techniques such as DPOR
are still applicable in each.
Moreover, because Iterative Deepening treats the set of preemption points as mutable,
it can add new preemption points reactively based on any runtime analysis.
Here
will focus on run-time data race analysis~\cite{tsan,fasttrack} as the mechanism for finding new preemption candidates.
The next section (\cref{sec:quicksand-soundness})
will prove that in fact,
in addition to statically-known synchronization preemption points,
this suffices to provide at least as strong verification guarantees as any other possible preemption point set.

@@

Given unlimited CPU time for testing,
one would always want to switch to the new maximal state space whenever adding a new preemption point.
The maximal state space is guaranteed to subsume all execution sequences reachable in any subset state space,
so considering any incomplete subset of the known preemption points would be redundant work.
\Cref{alg:algorithm0} demonstrates this na\"ive approach.
It is seeded with the set of all statically-known synchronization API preemption points,
and invoked whenever a new data-race candidate is found.
%
The upcoming proofs in \cref{sec:quicksand-soundness},
being concerned with the verification guarantee provided when the search may complete within the CPU budget,
are based on this simple version of Iterative Deepening.
The user may also wish to configure her testing tool to prefer this approach, at her discretion,
such as when she believes all bugs have been fixed and wants a verification as fast as possible;
% TODO: clarify sec reference to -M flag
\cref{sec:quicksand-implementation} discusses this execution mode further.

@@

\begin{figure}[t]
        %\includegraphics[width=0.48\textwidth]{dr-jobs-v2.pdf}
        asdfsaf
        % TODO: put the figure form yr snake fight
	\caption[Quicksand incorporates data races as new preemption points at run-time.]
		{Quicksand incorporates data races as new preemption points at run-time,
		by managing the exploration of multiple state spaces,
		communicating with each MC instance to receive ETAs, data race candidates, and bug reports.
                %When an access pair is reported as a data race candidate,
                When a data race is reported,
                a new preemption point is added for each involved access,
                and new jobs are added for later testing,
                corresponding to different combinations of those with the existing preemption points.}
        \label{fig:new-dr-jobs}
\end{figure}

@@

% TODO: fix syntax hilight
% TODO check figure placement
% TODO check figure camption
\begin{figure}[t]
	\begin{center}
	\begin{tabular}{rll}
		& \multicolumn{2}{c}{\texttt{struct x \{ int foo; int baz; \} *x;}} \\
		& \multicolumn{2}{c}{\texttt{struct y \{ int bar; \} *y;~~~~~~~~~~}} \\
		\\
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		2 & \texttt{\hilight{olivegreen}{free}(x);} \\
		3 & & \texttt{\hilight{commentblue}{// x's memory reallocated}} \\
		4 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		5 & & \texttt{\hilight{commentblue}{// ...initialize...}}\\
		6 & & \texttt{publish(y);} \\
		7 & & \texttt{\hilight{brickred}{y->bar = ...;}} \\
	\end{tabular}
	\end{center}
	% TODO: short ver
	\caption{A common execution pattern with {\tt malloc()} that produces false positive data race candidates.}
	\label{fig:recycle}
\end{figure}

@@

% TODO smae as above
\begin{figure}[t]
	\begin{tabular}{rll}
		& {\bf Thread 1} & {\bf Thread 2} \\
		1 & \texttt{publish(x);} & \\
		2 & \texttt{\hilight{brickred}{x->foo = ...;}} & \\
		3 & \texttt{\hilight{olivegreen}{free}(x);} \\
		4 & & \texttt{x2 = get\_published\_x();} \\
		5 & & \texttt{\hilight{commentblue}{// x's memory recycled}} \\
		6 & & \texttt{y~=~\hilight{olivegreen}{malloc}(sizeof *y);} \\
		7 & & \texttt{\hilight{brickred}{x2->foo = ...;}} \\
	\end{tabular}
	% TODO: shortver
	\caption{If a single-pass Limited HB analysis discarded candidates matching the malloc-recycle pattern,
it would miss the bug in this adversarial program.}
	\label{fig:recycle-bug}
\end{figure}

@@

% TODO: check spcaing between defs/lemmas/etc and surrounding text
\begin{definition}[Reachability]
	A data race candidate, and its associated preemption point(s),
	are reachable if it will be identified by a model checker
	configured to preempt only on already-reachable preemption points.
\end{definition}

@@

\begin{itemize}
	\item {\bf Single state space, basic DPOR} ({\tt -C}):
		Runs a single instance of Landslide configured to preempt on all statically-known synchronization PPs.
		Corresponds to dBug's approach \cite{dbug-ssv}.
		Never adds any new preemption points based on data race reports.
	\item {\bf Single state space, ICB} ({\tt -I}):
		Runs a single instance of Landslide with preemption points as above,
		but running Iterative Context Bounding with BPOR (\cref{sec:landslide-icb})
		instead of plain DPOR.
		Corresponds to CHESS's approach \cite{chess}.
		Requires either {\tt -C} or {\tt -M} (see below).
	\item {\bf Single state space, preempt-everywhere} ({\tt -0}):
		Runs a single instance of Landslide as above,
		but preempting on every shared memory access, not just synchronization.
		Corresponds to the approach of SPIN \cite{spin} and Inspect \cite{inspect};
		CHESS supports this mode as well with optional compiler instrumentation.
		Requires {\tt -C}; may optionally be combined with {\tt -I}.
	\item {\bf Maximal state space mode} ({\tt -M}):
		Runs the na\"{i}ve version of Iterative Deepening shown in \Cref{alg:algorithm0},
		i.e.,
		immediately abandons any state space whenever a superset of it exists.
		This results in always testing the maximal state space only, with no inherent parallelism,
		and optimizes for the fastest verification when the user has reason to believe no bugs will exist.
		No prior work implements this approach.
		Note that this mode was implemented after \cite{quicksand}'s publication,
		and I will feature it in the evaluation of transactional memory
		(\cref{sec:tm-eval}) rather than in this chapter.
\end{itemize}

@@

Preempt-everywhere mode (\cref{sec:quicksand-impl-modes})
imposes a heavy burden on Landslide on account of the sheer number of preemption points involved.
First of all, because there are separate tracing entrypoints for memory accesses and instructions ({\tt instrument.c}),
it cannot simply invoke the checkpointing routine (\cref{sec:landslide-timetravel}) immediately.
Also, we must still exclude thread-local and kernel (if testing userspace) or user (if testing kernelspace) accesses.
Rather,
the memory analysis (\cref{sec:landslide-memory}) invokes
{\tt maybe\_preempt\_here()} in {\tt pp.c}
for every access it would ordinary record for DPOR.
If the access is outside of the current stack frame,
and not part of the mutexes (unless {\tt TESTING\_MUTEXES}),
this sets a scheduler action flag {\tt preempt\_for\_shm\_here}
which makes preemption point identification treat it the same as a data race (\cref{sec:landslide-pps}).
{\tt check\_withins()} is also modified to never switch to allowlist mode.
Finally,
Landslide increases its heuristic constant for infinite loop detection (\cref{sec:landslide-infloop})
on the first interleaving from 4000 to $2^{20}$,
to account for the increased orders of magnitude in preemptible events.

@@

% TODO: introd this

I pose the following evaluation questions.

\begin{enumerate}
	\item Does integrating data-race preemption points improve the accuracy of model checking?
		\begin{enumerate}
			\item Do data-race preemption points expose new bugs that couldn't be found with
				synchronization ones alone?
			\item Do data-race preemption points expose the same bugs
				the preempt-everywhere approach could find, faster?
			\item Does Quicksand provide more full verifications %of bug-free programs
				more quickly than the preempt-everywhere approach?
			% not related to new phrasing of Q1, and also the answer is "kinda sorta not really sometimes" anyway
			%\item Does Iterative Deepening find bugs faster in subset state spaces,
			%	even without data-race preemption points?
			\item How does the choice between Pure and Limited Happens-Before
				affect bug-finding and verification performance?
		\end{enumerate}
	\item Does testing alternate interleavings with model checking improve the accuracy of data race analysis?
		\begin{enumerate}
			\item Does Quicksand avoid false positives compared to single-execution Limited Happens-Before?
			\item Does Quicksand find data-race bugs that single-execution Pure or Limited Happens-Before would miss?
		\end{enumerate}
\end{enumerate}

\subsubsection{Test suite}

The test suite consists of 79 P2 student thread libraries (\cref{sec:pebbles}),
submitted in 15-410 during the Spring 2014, Fall 2014, and Spring 2015 semesters,%
\footnote{The 2014 semesters were before \Cref{chap:education}'s user study experiments,
and for Spring 2015 (the first semester thereof),
students who used Landslide during the project were excluded from this dataset.}
and 78 Pintos student kernels (\cref{sec:overview-pintos}),
submitted in Berkeley's CS162 and U. Chicago's CMSC 23000 during Spring 2015.
The P2s in this dataset average 1807 lines of C and x86 assembly code,
%, with a standard deviation of 489.5, % i don't know where hte pintos stdev went and i don't wanna recalc it
and the Pintoses average 718 lines (by {\tt diff} to the provided basecode),
for a total of 198,772 lines of code tested for this evaluation.

I chose P2s and Pintoses for this test suite because of the relative ease of generating hundreds of unique state spaces,
varied in size and correctness, and with a diverse set of bug types.
In addition to concurrency bugs,
many of the codebases exhibited {\em deterministic} bugs (i.e., encountered on the first interleaving tested),
which I fixed by hand before running these tests to ensure that every bug in this study required meaningful work by the model checker.
While many prior work stateless model checking papers
% TODO: cite some
publish studies of single-digit or low-double-digit numbers of
bugs found in ``real-world'' programs, often confirmed by the upstream developers as severe,
to motivate stateless model checking to be used in production settings,
I believe this approach to be too anecdotal for comparing several model checking strategies {\em against each other},
and opt for this approach instead for better statistical significance.%
\footnote{Not to mention -- as I couldn't say in a conference paper, but can say now --
that extending Landslide to support native Linux programs,
complete with filesystem and network nondeterminism,
would have been an engineering burden beyond my ability to do alone and still graduate on time.}

\newcommand\mxtest{\texttt{mx\_test}}
\newcommand\tej{\texttt{join\_test}}
\newcommand\bct{\texttt{bcast\_test}}
\newcommand\paraguay{\texttt{signal\_test}}
\newcommand\paradise{\texttt{sem\_test}}
\newcommand\rwldgr{\texttt{rwlock\_test}}
\newcommand\prisema{\texttt{sched\_test}}
\newcommand\waitsimple{\texttt{wait\_test}}
\newcommand\alarmsimul{\texttt{alarm\_test}}

I tested P2s with 6 multithreaded programs:
\mxtest, for locking algorithm correctness,
\tej, a test of thread lifecycle,
\bct~and \paraguay~for condition variables,
\paradise~for semaphores,
% nb: there used to be a "f u latex" comment here with a \\ after dgr, prob for margins
and \rwldgr for r/w locks.
These are the same tests I distributed Landslide with in \Cref{chap:education};
\cref{sec:education-pebbles-tests} describes them in further detail.
For \mxtest, \paradise, and \paraguay,
I used the {\tt without\_function} command to exclude {\tt thr\_create}, {\tt thr\_exit}, and {\tt thr\_join} preemption points,
and for \mxtest I enabled {\tt TESTING\_MUTEXES} (\cref{sec:landslide-dynamicconfig}).
I tested Pintoses with 3 programs from the class's provided test suite:
\prisema, a test of the kernel scheduling algorithm,
\alarmsimul, for the timer sleep routine,
and \waitsimple, for process lifecycle system calls.
These are a subset of those used in \Cref{chap:education}; see \cref{sec:education-pintos-tests}.
Some of the Pintoses were partially implemented,
so each test could only be run on a subset of the 78 submissions;
see the ``Number tested'' column in \Cref{tab:drbugs}.
For all tests,
I also excluded preemption points on {\tt malloc}'s internal lock using {\tt without\_function}.
In total, the evaluation comprises 629 unique tests (i.e., pairs of a test program and a Pintos or P2),
at least 181 of which will be seen to expose bugs.

\subsubsection{Experimental setup}

To evaluate the benefits of data-race preemption points and Iterative Deepening separately,
I ran the test suite under Quicksand in three different experimental configurations,
each of which was given a 1-hour budget and 10 CPUs for each test.

\begin{itemize}
	\item {\bf QS-Limited-HB}: Quicksand with Landslide configured to use Limited Happens-Before for its data race analysis ({\tt -H}),
	\item {\bf QS-Pure-HB}: Quicksand using Pure Happens-Before instead ({\tt -V}), and
	\item {\bf QS-Sync-Only}: Quicksand with initial preemption points only \cref{sec:quicksand-initial-pps},
		but never adding new ones from reported data races.
\end{itemize}

I represented the MC State of the Art%
\footnote{The author's DJ name.}
with three configurations of stand-alone Landslide on the same test suite,
corresponding to the search strategies discussed in \cref{sec:quicksand-impl-modes} and \cref{sec:quicksand-impl-landslide}.

\begin{itemize}
	\item {\bf SSS-MC-DPOR}: Single state space mode ({\tt -C})
		using the maximal preemption point set from \cref{sec:quicksand-initial-pps},
		explored with DPOR (\cref{sec:landslide-dpor}),
		%From prior work, dBug \cite{dbug-ssv} implements this approach, among others. %% nb -- already discussed above
        \item {\bf SSS-MC-ICB}: With preemption points as above,
		but instead using ICB \cite{chess-icb} with BPOR \cite{bpor} to find bugs faster
		({\tt -I}, \cref{sec:landslide-icb}), and
		%From prior work, CHESS \cite{chess} implements this approach.
        \item {\bf SSS-MC-Shared-Mem}:
		Using ICB+BPOR, configured to preempt on any shared memory access ({\tt -0}).
                (decided at runtime, excluding threads' accesses to their own stacks),
                which in principle includes all possible data races.
		%From prior work, Inspect \cite{inspect} implements this approach,
		%and CHESS also supports this mode with optional compiler instrumentation.
\end{itemize}

Prior work has shown how to parallelize DPOR of a single state space across multiple processors \cite{parallel-dpor},
but it remains an open research problem how to extend the algorithm to ICB.
Hence, I optimistically gave control experiments a linear speedup of 10 hours per test with 1 CPU;
i.e., assuming it could parallelize with 100\% efficiency.
To match this,
Quicksand reports the CPU-time spent in addition to the wall-clock time for a resource-fair comparison,
although Quicksand's inherent parallelism is a convenient benefit unto itself.
All tests ran on 12-core 3.2 GHz Xeon W3670 machines with 12GB of RAM.
